\documentclass[12pt,a4paper]{article}
% ===== Packages =====
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,fit,backgrounds}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\graphicspath{{../}{./}}
\geometry{margin=2.5cm}

% ===== Macros =====
\newcommand{\Dw}{D_{\mathrm{w}}}
\newcommand{\Ddw}{D}
\newcommand{\Dpv}{D_{\mathrm{PV}}}
\newcommand{\Cinv}{C^{-1}}
\newcommand{\Cpvinv}{C_{\mathrm{PV}}^{-1}}
\newcommand{\Aop}{A}
\newcommand{\PL}{P_{L}}
\newcommand{\Pp}{P_{+}}
\newcommand{\Pm}{P_{-}}
\newcommand{\dg}{^{\dagger}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}

\title{\textbf{A Pauli--Villars Preconditioned, Aggregation-Based\\
Algebraic Multigrid Solver for the M\"obius Domain-Wall Operator}}
\author{Wei-Lun Chen, Kanamori Issaku, Matsufuru Hideo}
\affil{\small (working note, Bridge++ \texttt{with\_alpha} branch)}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We document the operator and the solution algorithm used in the present
Bridge++ implementation of an algebraic multigrid (AMG) solver for the M\"obius
domain-wall (DW) fermion, together with all parameters of the test problem. The
bare DW operator $\Ddw$ is non-normal and its spectrum straddles the imaginary
axis, so Krylov methods applied directly to $\Ddw$ converge poorly. Following
Kanamori, Chen and Matsufuru [PoS(LATTICE2024)414] we instead solve the
Pauli--Villars (PV) and site-diagonal preconditioned operator
$\Aop=(\Dpv\,\Cpvinv)\dg\,\Cinv\,\Ddw$, whose spectrum lies in the open right
half-plane. A left-preconditioning identity makes the solution of
$\Aop$ return $\Ddw^{-1}b$ exactly. The outer iteration is a flexible GMRES
(FGMRES) on $\Aop$, preconditioned by a two-grid V-cycle (a fixed-iteration
GMRES-on-$\Aop$ smoother and an $\Aop$-Galerkin coarse-grid correction
built from chirality-split, block-orthonormalised near-null vectors). We give the
complete operator definitions,
the algorithm, the full set of test parameters, and a \emph{residual-matched}
iteration-count comparison against the production even-odd CGNE solver and against
unpreconditioned GMRES on $\Aop$. We emphasise that the near-null-space setup is
deliberately minimal in this run; the comparison therefore understates what the
method can reach, and is reported as a correctness-and-feasibility baseline.
\end{abstract}

\section{The M\"obius domain-wall operator}
\label{sec:operator}

We work with the five-dimensional M\"obius domain-wall operator $\Ddw$ with a
Wilson kernel. Let $\Dw(M_0)$ be the four-dimensional Wilson--Dirac operator with
negative mass (domain-wall height) $-M_0$, written through the hopping parameter
$\kappa = 1/(8-2M_0)$. $\Dw$ is an \emph{eight-point} nearest-neighbour stencil,
\begin{equation}
(\Dw\psi)(x) = \psi(x) - \kappa\sum_{\mu=1}^{4}\Big[
(1-\gamma_\mu)U_\mu(x)\psi(x+\hat\mu)
+ (1+\gamma_\mu)U_\mu\dg(x-\hat\mu)\psi(x-\hat\mu)\Big],
\end{equation}
i.e.\ two hops ($\pm\hat\mu$) in each of the four spacetime directions per site.
Let $s=0,\dots,N_s-1$ index the fifth dimension of extent $N_s$. With
$P_\pm=\tfrac12(1\pm\gamma_5)$ the M\"obius operator parameterised by $(b,c)$ acts
on a five-dimensional spinor $\psi_s$ as
\begin{equation}
(\Ddw\,\psi)_s
= \big(b\,\Dw + 1\big)\,\psi_s
\;+\; \big(c\,\Dw - 1\big)\!\left[ \Pm \,\psi_{s+1} + \Pp\,\psi_{s-1} \right],
\end{equation}
with the mass-carrying wrap $\psi_{N_s} = -m_q \Pm \psi_0$,
$\psi_{-1} = -m_q \Pp \psi_{N_s-1}$. The fifth-dimension coupling carries no gauge
links, so \textbf{one application of $\Ddw$ costs $N_s$ four-dimensional
eight-point Wilson hops} (plus the cheap tridiagonal $\pm\gamma_5$ shift). The
Pauli--Villars operator is the same operator at unit mass,
$\Dpv \equiv \Ddw\big|_{m_q\to1}$.

The DW operator carries an exactly site-diagonal (in the four-dimensional sense)
factor $C$ in the fifth dimension --- the $N_s\times N_s$ tridiagonal block that
is local in spacetime. Its inverse $\Cinv$ is computed \emph{exactly} by
forward/back substitution (LU of the $N_s$-block, the Bridge++ \texttt{Prec} mode
$L^{-1}\!\circ U^{-1}$); $\Cpvinv$ is the same for the PV operator. These factors
are site-local: they cost \emph{no} four-dimensional hop. No iterative solver and
no double-precision promotion is used for any of them.

The parameters of the test problem are collected in Table~\ref{tab:params}.

\begin{table}[h]
\centering
\begin{tabular}{lll}
\toprule
quantity & symbol & value \\
\midrule
lattice volume        & $L^3\times T$    & $12^4$ \\
gauge action          &                  & quenched Wilson, $\beta=5.7$ \\
configuration         &                  & quenched HMC, plaquette $0.560$ \\
fifth-dimension extent& $N_s$            & $8$ \\
domain-wall height    & $M_0$            & $1.0$ \\
M\"obius coefficients & $(b,c)$          & $(1.5,\,0.5)$ \\
quark mass            & $m_q$            & $0.005$ \\
PV mass               & $m_{\mathrm{PV}}$& $1.0$ \\
Neff's alpha          & $\alpha$         & $1.0$ \\
boundary conditions   &                  & $(1,1,1,-1)$ \\
\bottomrule
\end{tabular}
\caption{Operator and gauge parameters of the test problem.}
\label{tab:params}
\end{table}

\section{The preconditioned target operator}
\label{sec:target}

The bare operator $\Ddw$ is non-normal: its eigenvalues have both signs of real
part, and unpreconditioned GMRES/FGMRES stagnate. We therefore form the positive
(right-half-plane) target operator of Ref.~\cite{KCM2024},
\begin{equation}
\boxed{\;\Aop \;=\; \big(\Dpv\,\Cpvinv\big)\dg\;\Cinv\;\Ddw\;}
\label{eq:A}
\end{equation}
in which all four factors are applied exactly. The mechanism is that of
Brower, Clark, Howarth and Weinberg \cite{BrowerPV}: left-multiplying the
non-normal $\Ddw$ by $(\Dpv\Cpvinv)\dg$ rotates its sign-straddling spectrum into
the open right half-plane, which is what allows a Krylov method to converge on
$\Aop$ where it stagnates on $\Ddw$. Since $\Cinv$ and
$\Cpvinv$ are site-local, \textbf{one application of $\Aop$ costs two
four-dimensional hopping sweeps} (one through $\Ddw$, one through $\Dpv\dg$), i.e.\
$2N_s = 16$ eight-point Wilson hops on the present lattice.

\paragraph{Left preconditioning.}
Define the left-preconditioner
$\PL = (\Dpv\,\Cpvinv)\dg\,\Cinv$, so that $\Aop = \PL\,\Ddw$. To solve the
physical system $\Ddw\,x = b$ we solve instead
\begin{equation}
\Aop\,x = b', \qquad b' = \PL\,b ,
\label{eq:leftprec}
\end{equation}
because $\Aop x = \PL b \iff \PL(\Ddw x - b)=0$ and $\PL$ is non-singular; the
solution is $x = \Ddw^{-1}b$ exactly. The inner and physical residuals are related
by $b'-\Aop x = \PL(b-\Ddw x)$. \textbf{This relation is essential to a fair
comparison: $\PL$ is ill-conditioned, so a small residual on $\Aop$ does not imply
a small physical residual $\norm{b-\Ddw x}$.} We therefore always drive and report
the \emph{physical} relative residual $\norm{b-\Ddw x}/\norm{b}$ when comparing
solvers, never the $\Aop$-residual alone.

\paragraph{Inheritance and lineage.} The construction of this section --- the
Pauli--Villars target operator $\Aop$, the exact site-local $\Cinv$ via the
$\texttt{Prec}$ ($L^{-1}U^{-1}$) mode, the left-preconditioning identity, and the
5D--4D chiral source/sink used to carry the physical propagator on the boundary
walls --- follows the design note of Kanamori, Chen and Matsufuru \cite{KCM2024}.
That note is itself the domain-wall specialisation of the adaptive aggregation
multigrid implemented in Bridge++ for the Wilson--Clover operator
\cite{BridgeMG}, which in turn follows the DD-$\alpha$AMG method of Frommer
\emph{et al.}\ \cite{DDalphaAMG}; the idea of preconditioning the non-normal
domain-wall operator with the Pauli--Villars operator so that the spectrum is
pushed into the open right half-plane is due to Brower, Clark, Howarth and
Weinberg \cite{BrowerPV}. The present work implements this construction in
Bridge++ and builds the batched aggregation multigrid of
Section~\ref{sec:algorithm} on top of it.

\section{The multigrid algorithm}
\label{sec:algorithm}

The solver is an aggregation-based two-grid algebraic multigrid acting on the
positive operator $\Aop$. The outer Krylov method is \emph{flexible} GMRES, which
is required because the V-cycle preconditioner is not a fixed linear operator.

\subsection{Aggregates, near-null space and the transfer operators}
The fine lattice is partitioned into non-overlapping blocks (aggregates) of size
$3^4$ in spacetime (the full $N_s$ is kept in the fifth dimension), giving a
coarse lattice of $4^4$ sites on the $12^4$ volume. A set of $N_v=8$ near-null
vectors $\{w_k\}$ is generated in the setup phase by the procedure of the design
note \cite{KCM2024,BridgeMG}: starting from random vectors, the smoother is
applied and the multigrid preconditioner is then applied recursively a few times,
so the vectors are driven towards the near-null space of $\Aop$. Within each
aggregate the vectors are split by chirality and \emph{block orthonormalised}. The
relevant chirality for the domain-wall operator is $\Gamma_5 = \mathcal{R}\,\gamma_5$,
where $\mathcal{R}$ is the reflection in the fifth dimension, and the projector is
$\tfrac12(1\pm\Gamma_5)$ (the first-choice projection of \cite{KCM2024}); the
split doubles the coarse degrees of freedom to $2N_v=16$ per aggregate. This
defines the prolongation $P$ (piecewise span of the orthonormal block vectors) and
the restriction $R = P\dg$.

\paragraph{Block orthonormalisation.}
The block Gram--Schmidt is performed by a \emph{batched classical} Gram--Schmidt
(CGS): for each target vector all block inner products against the
already-accepted vectors are computed in one batched kernel, subtracted in one
batched \texttt{axpy}, and the block is normalised. A single CGS pass is used. A
second (re-)orthogonalisation pass is \emph{not} applied: the projector basis
carries two chiralities ($\norm{w_k}^2_{\text{block}}=2$, one from $\Pm$ and one
from $\Pp$), and a naive second pass mixes the chirality sectors and destroys the
orthogonality established by the first pass. The single batched CGS pass
reproduces the modified-Gram--Schmidt result to working precision at $O(1)$ kernel
launches per target vector.

\begin{algorithm}[H]
\caption{Setup: near-null space and transfer operators (run once, before the solve).}
\label{alg:setup}
\begin{algorithmic}[1]
\State draw $N_v$ random fine vectors $\{w_k\}$
\For{$k=1,\dots,N_v$}
  \State $u \gets \mathrm{GMRES}_4(\Aop,\,w_k)$ \Comment{smoother: $u\approx\Aop^{-1}w_k$ (Alg.~\ref{alg:gmres})}
  \State $w_k \gets \Dpv\,u$ \Comment{map through the Pauli--Villars operator (mode ``D'')}
\EndFor
\For{$n=1,\dots,N_{\mathrm{step}}$} \Comment{adaptive enrichment; $N_{\mathrm{step}}=0$ here, so skipped}
  \State $w_k \gets \Dpv\,M^{-1}w_k$ for all $k$;\quad rebuild $P,R,\Aop_c$ below
\EndFor
\State $(P,R) \gets \textsc{BuildTransfer}(\{w_k\})$ \Comment{Alg.~\ref{alg:transfer}}
\State $\Aop_c \gets R\,\Aop\,P$ \Comment{Galerkin coarse operator (nearest-neighbour truncated)}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsc{BuildTransfer}: chirality split and block orthonormalisation
$\Rightarrow P,R$.}
\label{alg:transfer}
\begin{algorithmic}[1]
\State $\Gamma_5 \gets \mathcal{R}\,\gamma_5$ \Comment{$\mathcal{R}$ = reflection in the fifth dimension}
\For{$k=1,\dots,N_v$} \Comment{chirality split: $N_v \to 2N_v$ candidates}
  \State $w_k^{+}\gets\tfrac12(1+\Gamma_5)\,w_k$;\quad $w_k^{-}\gets\tfrac12(1-\Gamma_5)\,w_k$
\EndFor
\For{each aggregate (block) $\Omega_b$ of size $3^4\times N_s$}
  \State restrict the $2N_v$ candidates to $\Omega_b$
  \State batched classical Gram--Schmidt (single pass) $\Rightarrow$ orthonormal block basis $\{b_{b,1},\dots,b_{b,2N_v}\}$
\EndFor
\State $P:$ coarse dof $(b,\ell)\mapsto b_{b,\ell}$ supported on $\Omega_b$ (piecewise span);\quad $R\gets P\dg$
\end{algorithmic}
\end{algorithm}

\paragraph{Coarse operator and its stencil locality.}
The coarse-grid operator is the Galerkin projection of $\Aop$,
$\Aop_{c} = R\,\Aop\,P = P\dg\,\Aop\,P$, assembled explicitly so the coarse solve
never touches the fine grid. The coarse problem is solved approximately by
restarted GMRES (loose tolerance $10^{-2}$, at most two iterations), which is
adequate inside a V-cycle.

The defining design axis among domain-wall multigrid methods is the
\emph{hopping range (stencil locality) of the coarse operator}, which sets the
cost of building and applying $\Aop_c$. The squared red-black operator used by
HDCG produces a coarse stencil reaching all points of taxicab distance up to
four --- a $321$-point four-dimensional stencil (only reduced to $81$ points at a
minimum $4^4$ block), so re-evaluating the little Dirac operator along an HMC
trajectory costs thousands of fine multiplies. The recent multiple-right-hand-side
domain-wall multigrid \cite{BoyleMRHS} likewise adopts a \emph{four-hop} coarse
operator. At the
opposite end, a \emph{zero-hop} (purely block-diagonal, no inter-aggregate
coupling) coarse approximation is the cheapest but discards the long-wavelength
coupling that gives multigrid its mass/volume independence. \textbf{Our coarse
operator is a one-hop (nearest-neighbour) coarse Dirac operator}
(\texttt{AFopr\_Domainwall\_coarse}): the Galerkin projection of the
PV-preconditioned $\Aop$ is truncated to a nearest-neighbour stencil, which
preserves sparsity (and hence recursive coarsenability) at a small fraction of
the assembly cost of the four-hop stencils, while retaining the inter-aggregate
coupling absent from the zero-hop choice. This is the nearest-neighbour-truncated,
right-preconditioned coarse operator of the design note \cite{KCM2024}. A general
comparison of these domain-wall multigrid coarsening strategies is given by Boyle
and Yamaguchi \cite{BoyleYamaguchi}.

\subsection{Smoother}
The smoother is a fixed-iteration GMRES on the single-precision operator $\Aop$:
one GMRES($m$) cycle with $m=4$ Arnoldi vectors and a zero initial guess, applied
to the V-cycle residual to damp the high-frequency error the coarse grid cannot
represent (stopping criterion $10^{-3}$). Because $\Aop$ is non-Hermitian
--- its spectrum fills the right half-plane rather than a real interval --- a
Krylov smoother is the natural choice: GMRES builds the optimal residual polynomial
over the actual (complex) spectrum at each application, with no eigenvalue estimate
or relaxation parameter to tune, unlike a Chebyshev or damped-Jacobi sweep that
presupposes a real spectral interval. (A CGNR-on-$\Ddw$ smoother diverges at small
$m_q$ with $M_0=1$, the near-critical regime the PV preconditioning is designed to
avoid; GMRES-on-$\Aop$ is robust there.) The smoother strength --- here the GMRES
depth $m$ --- is the dominant convergence lever of the V-cycle, as quantified in
Section~\ref{sec:scaling}.

\begin{algorithm}[H]
\caption{$\mathrm{GMRES}_m(\Aop,b)$: $m$ Arnoldi steps with a zero initial guess,
returning $x\approx\Aop^{-1}b$. The smoother is one cycle with $m=4$; the coarse
solver runs the same routine with $m=5$ for at most two restart cycles, to
tolerance $10^{-2}$.}
\label{alg:gmres}
\begin{algorithmic}[1]
\State $\beta \gets \norm{b}$,\quad $v_1 \gets b/\beta$
\For{$j=1,\dots,m$}
  \State $w \gets \Aop\,v_j$
  \For{$i=1,\dots,j$} \Comment{Arnoldi (modified Gram--Schmidt)}
    \State $h_{ij}\gets(v_i,w)$;\quad $w \gets w - h_{ij}\,v_i$
  \EndFor
  \State $h_{j+1,j}\gets\norm{w}$;\quad $v_{j+1}\gets w/h_{j+1,j}$
\EndFor
\State $y \gets \arg\min_{y}\,\norm{\beta\,e_1 - \bar H\,y}$ \Comment{$(m{+}1)\times m$ least squares, Givens}
\State \Return $x \gets V_m\,y$, \quad $V_m=[v_1,\dots,v_m]$
\end{algorithmic}
\end{algorithm}

\subsection{The V-cycle and the outer iteration}
One application of the preconditioner $M^{-1}\approx\Aop^{-1}$ is a two-grid
V-cycle:

\begin{algorithm}[H]
\caption{Two-grid V-cycle $M^{-1}$ applied to a vector $r$ (returns $z$)}
\label{alg:vcycle}
\begin{algorithmic}[1]
\State $z \gets \text{GMRES}_4(\Aop, r)$ \Comment{pre-smoothing, GMRES depth $4$}
\State $r_c \gets R\,(r - \Aop\,z)$ \Comment{restrict the fine residual}
\State $e_c \gets \Aop_c^{-1} r_c$ \Comment{coarse solve (loose GMRES)}
\State $z \gets z + P\,e_c$ \Comment{prolongate the coarse correction}
\State $z \gets z + \text{GMRES}_4(\Aop,\, r - \Aop\,z)$ \Comment{post-smoothing, GMRES depth $4$}
\end{algorithmic}
\end{algorithm}

\noindent The complete solver is

\begin{algorithm}[H]
\caption{PV-preconditioned AMG solve of $\Ddw\,x=b$}
\begin{algorithmic}[1]
\State \textbf{Setup:} generate $N_v=8$ near-null vectors; chirality-split and
       block-orthonormalise (CGS); assemble $P,R,\Aop_c$.
\State $b' \gets \PL\,b$ \Comment{left-precondition: now solve $\Aop x = b'$}
\State Solve $\Aop\,x = b'$ by FGMRES (restart length $N_M=30$) using the V-cycle
       $M^{-1}$ as preconditioner, driving the \emph{physical} residual
       $\norm{b-\Ddw x}/\norm{b}$ to the target tolerance.
\State \Return $x = \Ddw^{-1}b$ \Comment{exact by the left-prec identity}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{$\mathrm{FGMRES}(\Aop,b,M^{-1})$ with restart length $N_M=30$: flexible
GMRES whose preconditioner $M^{-1}$ is the two-grid V-cycle (Alg.~\ref{alg:vcycle})
and is allowed to vary between steps. Returns $x\approx\Aop^{-1}b=\Ddw^{-1}b$.}
\label{alg:fgmres}
\begin{algorithmic}[1]
\State $x \gets 0$;\quad $r \gets b-\Aop x$;\quad $\beta\gets\norm{r}$;\quad $v_1\gets r/\beta$
\For{$j=1,\dots,N_M$}
  \State $z_j \gets M^{-1} v_j$ \Comment{apply the V-cycle; \emph{store} the preconditioned vector}
  \State $w \gets \Aop\,z_j$
  \For{$i=1,\dots,j$} \Comment{Arnoldi}
    \State $h_{ij}\gets(v_i,w)$;\quad $w\gets w-h_{ij}\,v_i$
  \EndFor
  \State $h_{j+1,j}\gets\norm{w}$;\quad $v_{j+1}\gets w/h_{j+1,j}$
\EndFor
\State $y\gets\arg\min_{y}\,\norm{\beta\,e_1-\bar H\,y}$;\quad $x\gets x + Z_{N_M}\,y$ \Comment{$Z=[z_1,\dots,z_{N_M}]$, \emph{not} $V$ --- the ``flexible'' step}
\State restart from the current $x$ until $\norm{b-\Ddw x}/\norm{b}<\text{tol}$
\end{algorithmic}
\end{algorithm}

\noindent In the residual-matched reference run of Table~\ref{tab:results} the
grid-transfer and coarse-grid work is in single precision (\texttt{float}) and the
outer FGMRES and the operator $\Aop$ are applied in double. The batched propagator
of Section~\ref{sec:batched} runs $\Aop$ and the entire V-cycle in single
precision, with double precision confined to an optional, runtime-selectable outer
residual.

\paragraph{Setup parameters and a caveat.}
Table~\ref{tab:mg} lists the multigrid parameters. \textbf{The near-null-space
setup is deliberately minimal here: the number of setup smoothing steps is
$N_{\mathrm{step}}=0$}, so the $N_v=8$ vectors are used essentially as generated,
without the iterative enrichment (applying the smoother to random vectors) that a
tuned aggregation setup performs. The coarse space is therefore \emph{not}
adapted to the near-null modes of $\Aop$, which is expected to leave a sizeable
part of the achievable speed-up on the table. Optimising the setup
($N_{\mathrm{step}}>0$, more vectors $N_v$, possibly more grid levels) is the
natural next step and requires more device memory and throughput than the single
consumer GPU used here.

\begin{table}[h]
\centering
\begin{tabular}{lll}
\toprule
component & parameter & value \\
\midrule
aggregate (block) & spacetime $\times$ fifth dim & $3^4 \times N_s$ \\
coarse lattice    &                              & $4^4$ \\
near-null vectors & $N_v$                        & $8$ \\
coarse dof / site & $2N_v$ (chirality split)     & $16$ \\
setup smoothing   & $N_{\mathrm{step}}$          & $0$ (unoptimised) \\
block orthog.     &                              & batched CGS, single pass \\
smoother          &                              & GMRES-on-$\Aop$, depth $4$, tol $10^{-3}$ \\
coarse solver     &                              & GMRES, depth $5$, $\le2$ cycles, tol $10^{-2}$ \\
outer solver      &                              & FGMRES, restart $N_M=30$ \\
grid transfer / coarse prec. &                   & single (\texttt{float}) \\
\bottomrule
\end{tabular}
\caption{Multigrid setup and cycle parameters.}
\label{tab:mg}
\end{table}

\section{Reference solvers}
\label{sec:reference}
We compare against two baselines that solve the \emph{same} physical propagator,
with the \emph{same} 5D--4D chiral source/sink construction:
\begin{itemize}
\item \textbf{Even-odd CGNE} on the normal equation $\Ddw\dg\Ddw$ --- the
production domain-wall solver, run in standard precision.
\item \textbf{Unpreconditioned GMRES on $\Aop$} --- restarted GMRES applied to the
identical target operator \eqref{eq:A} with the identical left-preconditioned
right-hand side, but \emph{without} the multigrid preconditioner. AMG and this
baseline differ \emph{only} by the V-cycle, so their comparison isolates the
preconditioner. Both wrap the inner $\Aop$-solve in the same outer
iterative-refinement on the physical residual (each step solves
$\Aop\,\delta=\PL\,r_{\mathrm{phys}}$, $x\!+\!=\!\delta$,
$r_{\mathrm{phys}}=b-\Ddw x$), so both reach the same physical tolerance.
\end{itemize}

\section{Batched, single-precision propagator through \texorpdfstring{$\Aop$}{A}}
\label{sec:batched}

The twelve colour--spin columns of the point-source propagator are solved through
$\Aop$ as a single multiple-right-hand-side (MRHS) block: a block-FGMRES outer
solver preconditioned by the batched V-cycle (batched $\Aop$-apply, restriction
and prolongation cast as small dense GEMMs, and a batched coarse block-FGMRES on
the Galerkin operator), with the physical propagator recovered by an outer
residual refinement built on the left-preconditioner. Because $\Aop=\PL\Ddw$, the
identity $\Aop^{-1}\PL=\Ddw^{-1}$ holds exactly, so a single refinement returns
the CGNE propagator up to the inner-solve tolerance. The entire V-cycle, the
$\Aop$-apply and the coarse solve run in FP32; double precision enters only the
optional outer residual, selected at runtime. On the single RTX~3080 the twelve
columns are processed in MRHS sub-batches of four --- a memory/throughput knob:
the full twelve-wide batch is throughput-optimal (one block solve, amortised
setup, maximal occupancy) but its block-Krylov basis and refinement scratch
exceed the $10$~GB device, whereas data-centre GPUs run the full batch.

\paragraph{The transfer operators as batched GEMMs.}
The cost of the V-cycle is dominated by the inter-grid transfers. For a single
right-hand side the restriction of the residual onto one aggregate is a set of
inner products against the $n_b$ near-null basis vectors,
\begin{equation}
  C_{j} \;=\; \sum_{x\in\text{block}}\sum_{a} \overline{(B_j)}_{a}(x)\, R_{a}(x)
  \;=\; \big(B\dg R\big)_j ,\qquad j=1,\dots,n_b ,
  \label{eq:restrict}
\end{equation}
a tall--skinny matrix--vector product of the $n_b\times K$ block-basis matrix
$B\dg$ with the $K$-vector $R$, where $K=(\text{block volume})\times N_{\mathrm{in}}$
is the number of fine degrees of freedom inside the aggregate. As a mat--vec this
is bandwidth-bound (flop/byte $\sim\!0.1$). Batching the $n_{\mathrm{rhs}}$
colour--spin columns turns the skinny mat--vec into a dense matrix--matrix product
\begin{equation}
  C\;[\,n_b\times n_{\mathrm{rhs}}\,]
  \;=\;
  B\dg\;[\,n_b\times K\,]\;\cdot\;R\;[\,K\times n_{\mathrm{rhs}}\,] ,
  \label{eq:restrictGEMM}
\end{equation}
one small GEMM per aggregate (Figure~\ref{fig:gemm}); the prolongation is the
transpose, $F=B\,C$. The aggregates are independent, so the V-cycle is a
\emph{batch} of independent small GEMMs --- compute-bound, and a direct match for
the warp-level MMA (tensor-core) tiles. The outer solver is a block-FGMRES that
carries all $n_{\mathrm{rhs}}$ columns through $\Aop$ and the V-cycle together,
adding a block-Krylov convergence gain on top of the throughput gain; its
small dense linear algebra (block Gram, Cholesky-QR, Hessenberg) is kept on the
device so no per-iteration host transfer occurs.

\begin{figure}[h]
\centering
\begin{tikzpicture}[font=\small, >=latex]
  % B^dagger : n_b x K
  \fill[blue!8] (0,0) rectangle (3.0,1.0);
  \draw[thick] (0,0) rectangle (3.0,1.0);
  \node at (1.5,0.5) {$B\dg$};
  \node[above] at (1.5,1.05) {\scriptsize $n_b \times K$};
  \node at (3.35,0.5) {$\times$};
  % R : K x n_rhs
  \begin{scope}[xshift=3.7cm]
    \fill[orange!12] (0,-0.6) rectangle (1.6,1.6);
    \draw[thick] (0,-0.6) rectangle (1.6,1.6);
    \foreach \x in {0.4,0.8,1.2} \draw[gray!60] (\x,-0.6) -- (\x,1.6);
    \fill[orange!40] (0,-0.6) rectangle (0.4,1.6);
    \node at (0.8,0.5) {$R$};
    \node[above] at (0.8,1.65) {\scriptsize $K \times n_{\mathrm{rhs}}$};
  \end{scope}
  \node at (5.75,0.5) {$=$};
  % C : n_b x n_rhs
  \begin{scope}[xshift=6.1cm]
    \fill[green!10] (0,0) rectangle (1.6,1.0);
    \draw[thick] (0,0) rectangle (1.6,1.0);
    \foreach \x in {0.4,0.8,1.2} \draw[gray!60] (\x,0) -- (\x,1.0);
    \fill[green!35] (0,0) rectangle (0.4,1.0);
    \node at (0.8,0.5) {$C$};
    \node[above] at (0.8,1.05) {\scriptsize $n_b \times n_{\mathrm{rhs}}$};
  \end{scope}
\end{tikzpicture}
\caption{Batched restriction on one aggregate, Eq.~\eqref{eq:restrictGEMM}. A
single right-hand side (the shaded column) is a tall--skinny mat--vec, bandwidth-
bound. Stacking the $n_{\mathrm{rhs}}$ colour--spin columns makes $R$ and $C$
``fat'', so the per-aggregate transfer becomes a dense GEMM that saturates the
tensor cores; the aggregates run as an independent batch. Prolongation is the
transpose $F=B\,C$.}
\label{fig:gemm}
\end{figure}

The resulting pseudoscalar correlator reproduces the production even-odd CGNE,
\[
  C_{PP}^{\mathrm{AMG}} = 1.56750\times10^{-1}, \qquad
  C_{PP}^{\mathrm{CGNE}} = 1.56754\times10^{-1},
\]
agreeing to $2.4\times10^{-4}$ --- the FP32 floor of the single-precision inner
solve, well below any physical scale: a quantitative, fully-batched check that
the batched $\Aop$ solve and the production CGNE return the same propagator.


\section{Numerical results}
\label{sec:results}

\paragraph{Setup.} Parameters of Tables~\ref{tab:params} and \ref{tab:mg}; single
NVIDIA RTX~3080. The two operator-$\Aop$ solvers (AMG, GMRES-on-$\Aop$) use the
\emph{identical} left-preconditioned right-hand side. All three solvers are driven
to a comparable \emph{physical} residual $\norm{b-\Ddw x}/\norm{b}\sim10^{-12}$,
so the iteration counts in Table~\ref{tab:results} are residual-matched.

\begin{table}[h]
\centering
\begin{tabular}{lccc}
\toprule
Solver & operator & outer iterations & $\norm{b-\Ddw x}/\norm{b}$ \\
\midrule
\textbf{AMG} (FGMRES + V-cycle) & $\Aop$ & \textbf{210} & $1.3\times10^{-12}$ \\
GMRES on $\Aop$ (no preconditioner) & $\Aop$ & $1202$ & $7.0\times10^{-13}$ \\
Even-odd CGNE (production) & $\Ddw\dg\Ddw$ & $\approx 333$ & $2.4\times10^{-12}$ \\
\bottomrule
\end{tabular}
\caption{Residual-matched iteration counts, $12^4$ $\beta=5.7$, $m_q=0.005$, all
at physical residual $\sim10^{-12}$. Against the identical-operator,
identical-right-hand-side GMRES baseline the V-cycle reduces the outer iteration
count by $\approx5.7\times$; against the production even-odd CGNE by
$\approx1.6\times$. The pseudoscalar correlators agree: the $\Aop$-based and CGNE
$C_{PP}(t)$ coincide to solver tolerance.}
\label{tab:results}
\end{table}

\paragraph{Reading the numbers honestly.}
Three caveats frame Table~\ref{tab:results}.
(i) The clean comparison is AMG versus unpreconditioned GMRES on $\Aop$: same
operator, same right-hand side, same physical tolerance, differing only by the
V-cycle ($5.7\times$). The CGNE column is the practical reference on a different
operator ($\Ddw\dg\Ddw$).
(ii) An outer AMG iteration (one V-cycle: GMRES smoothing $+$ coarse solve) is much
more expensive than a CGNE iteration, so the $1.6\times$ iteration advantage over
CGNE does \emph{not} translate into a wall-clock advantage on this small, coarse
problem --- and is not claimed to.
(iii) Most importantly, the near-null setup is unoptimised ($N_{\mathrm{step}}=0$,
$N_v=8$, two grid levels, single consumer GPU). A tuned setup is expected to
lower the AMG count substantially.

\paragraph{Where the V-cycle spends its time.}
Table~\ref{tab:vctime} breaks one V-cycle into its steps, accumulated over the
whole solve. (Absolute times on this WSL2/RTX~3080 host are unreliable --- the GPU
clock is not lockable --- but the \emph{proportions}, taken within a single
process and summed over ${\sim}200$ V-cycles, are robust.) The smoother dominates
at ${\sim}65\%$: it is two sweeps of $\mathrm{GMRES}_4$ on the full fine operator
$\Aop$. Counting operator applications, one V-cycle is ${\approx}9$ fine-$\Aop$
applies --- eight inside the two $\mathrm{GMRES}_4$ sweeps (four Arnoldi steps each)
and one in the residual --- so the smoother line is, almost entirely, fine-operator
time: ``smoother-limited'' means ``fine-$\Aop$-apply-limited''. The single
highest-leverage kernel is therefore the fine-operator application ($C^{-1}\Ddw$ and
the PV factor $\Dpv\Cpvinv$), which is exactly what the register-resident $C^{-1}$,
the fused $LU$ inverse, the $\gamma_5$-fold and the SU(3) third-row reconstruction
target. The coarse solve is $13\%$ and the two grid transfers together $18\%$; the
fine-grid residual and linear algebra are the remaining $4\%$. This quantifies
caveat~(ii): the V-cycle is \emph{smoother-limited}, so the convergence lever is
the smoother strength (Section~\ref{sec:scaling}), and the inter-grid transfers ---
cast as batched GEMMs in the production path (Section~\ref{sec:batched}), which is
relatively cheaper than the single-right-hand-side reference measured here --- are
not the bottleneck.

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
V-cycle step & time (s) & fraction \\
\midrule
smoother (two $\mathrm{GMRES}_4$ sweeps on $\Aop$) & $7.12$ & $\mathbf{65\%}$ \\
coarse solver                                       & $1.39$ & $13\%$ \\
restriction $R$                                     & $1.23$ & $11\%$ \\
prolongation $P$                                    & $0.81$ & $7\%$ \\
fine residual $+$ linear algebra                    & $0.44$ & $4\%$ \\
\midrule
V-cycle total                                       & $10.99$ & $100\%$ \\
\bottomrule
\end{tabular}
\caption{Per-step cost of one two-grid V-cycle, accumulated over the reference
solve ($12^4$, $m_q=0.005$, $\alpha=1$, single-RHS reference path). The smoother
(GMRES$_4$ on the fine $\Aop$, pre- and post-) is ${\sim}65\%$ of the cycle; the
coarse solve and the two transfers are the rest. Proportions, not absolute times,
are the meaningful quantity on this clock-unlocked host.}
\label{tab:vctime}
\end{table}

\paragraph{Where the value is.}
The textbook value of multigrid is that the outer iteration count is essentially
independent of the quark mass and the volume, whereas CGNE grows as $m_q\to0$ and
with the volume. Quantifying that scaling --- with an optimised near-null setup,
on larger volumes and smaller $m_q$, on hardware with the memory and throughput to
support it --- is the natural next step, and is the case for moving the study to a
supercomputer. The present run establishes correctness (matching $C_{PP}$ and
$m_{\mathrm{res}}$ across all three solvers) and a residual-matched baseline on a
single RTX~3080.

\section{Quark-mass scaling and solver tuning}
\label{sec:scaling}

The defining promise of multigrid is an iteration count that is nearly independent
of the quark mass, set against the growth of a Krylov solver as $m_q\to0$. We test
this directly on the batched solver by sweeping the bare quark mass
$m_q\in\{0.02,0.01,0.005,0.002,0.001\}$ at fixed $\alpha=0.5$ and recording the
outer iteration count of the AMG against that of the production even-odd CGNE.
For the AMG we report the outer V-cycle count of a single reference solve driven to
a fixed operator residual $\norm{\Aop x-b'}/\norm{b'}=10^{-13}$; for CGNE we report
the even-odd conjugate-gradient iteration count to physical residual
$\sim\!10^{-12}$, consistent with the CGNE column of
Table~\ref{tab:results}.\footnote{%
The two counts are convergence probes measured on different operators ($\Aop$
versus $\Ddw\dg\Ddw$) and, for the AMG, on the operator residual rather than the
physical residual of Section~\ref{sec:target}. They are \emph{not} the
residual-matched counts of Table~\ref{tab:results} (which drives the physical
residual to $\sim\!10^{-12}$ for both solvers, giving AMG~$210$ vs CGNE~$\approx
333$ at $m_q=0.005$); they are internally consistent across the sweep and used here
only to expose the mass-scaling \emph{trend}. The CGNE figure at $m_q=0.005$
($359$) agrees with the $\approx\!333$ of Table~\ref{tab:results} to the
granularity of the mixed-precision refinement cycles.} The results are in
Table~\ref{tab:massscan} and Figure~\ref{fig:massscan}.

\begin{table}[h]
\centering
\begin{tabular}{ccc}
\toprule
$m_q$ & AMG outer iters & CGNE iters \\
\midrule
$0.020$ & $245$ & $350$ \\
$0.010$ & $247$ & $355$ \\
$0.005$ & $247$ & $359$ \\
$0.002$ & $247$ & $361$ \\
$0.001$ & $254$ & $362$ \\
\bottomrule
\end{tabular}
\caption{Iteration count versus bare quark mass, $12^4$ HMC configuration,
$\alpha=0.5$ (AMG: outer V-cycles to $\Aop$-residual $10^{-13}$; CGNE: even-odd CG
iterations to physical residual $\sim\!10^{-12}$). Both solvers are essentially flat
across a $20\times$ range of $m_q$.}
\label{tab:massscan}
\end{table}

\begin{figure}[h]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=11cm, height=7cm,
    xmode=log, log basis x=10,
    xlabel={$m_q$}, ylabel={outer iterations},
    xmin=0.0008, xmax=0.025, ymin=0, ymax=560,
    grid=both, grid style={gray!20},
    legend pos=south west, legend cell align=left,
    tick label style={font=\small}, label style={font=\small},
]
\addplot[only marks, mark=*, mark size=2.2pt, red] coordinates {
  (0.020,350) (0.010,355) (0.005,359) (0.002,361) (0.001,362)
};
\addlegendentry{even-odd CGNE}
\addplot[only marks, mark=square*, mark size=2.2pt, blue] coordinates {
  (0.020,245) (0.010,247) (0.005,247) (0.002,247) (0.001,254)
};
\addlegendentry{PV-preconditioned AMG}
\end{axis}
\end{tikzpicture}
\caption{Outer iteration count versus bare quark mass ($12^4$, $\alpha=0.5$). Across
a $20\times$ range of $m_q$ \emph{both} solvers are nearly constant --- the AMG
varies by $4\%$ ($245\!\to\!254$) and CGNE by $3\%$ ($350\!\to\!362$). Neither
exhibits the textbook $m_q\to0$ growth.}
\label{fig:massscan}
\end{figure}

\paragraph{This flatness is a finite-volume effect, not a null result.}
On the present $12^4$ lattice the lowest eigenvalue of the Dirac operator is set by
the volume scale ($\sim\!1/L$), not by $m_q$: the spectral gap does not close as the
bare mass is lowered, so the conditioning of both $\Aop$ and $\Ddw\dg\Ddw$
saturates and the iteration counts plateau. The near-zero modes that drive CGNE's growth --- and against which
multigrid's mass-independence is the decisive advantage --- simply do not appear in
this regime. Exhibiting the separation therefore requires reaching genuinely small
effective mass: a larger physical volume (so the spectral gap can close) and/or a
larger $N_s$ (so $m_{\mathrm{res}}\ll m_q$). This is the central quantitative
motivation for moving the study to a supercomputer (Section~\ref{sec:future}). What
the present run does establish is that, even in this benign regime, the AMG already
runs below the production solver at every mass --- the residual-matched advantage is
the $\approx\!1.6\times$ of Table~\ref{tab:results} --- and that neither solver has
yet entered the regime where that gap can widen.

\paragraph{Solver tuning: the V-cycle is smoother-limited and already balanced.}
We swept the multigrid parameters at $m_q=0.005$, using the reference-solve outer
count as the objective (Table~\ref{tab:tuning}). The single effective convergence
lever is the GMRES smoother depth: raising it from $4$ to $8$ to $16$ Arnoldi
vectors cuts the outer count from $247$ to $150$ to $97$. That reduction is sub-linear in the
added smoother work, however, so the \emph{wall-clock} is minimised at four
sweeps --- fewer sweeps ($2$--$3$) and more sweeps ($8$--$16$) are both slower. The
other knobs are ineffective in this regime: adaptive setup smoothing
($N_{\mathrm{step}}>0$) leaves the count unchanged at $247$--$249$ while the
eigenvector-seeded near-null space is already adequate; enlarging the near-null
space ($N_v=8\!\to\!16$) buys only $247\!\to\!238$; tightening the coarse solve
($2\!\to\!10$ iterations) changes nothing, confirming the coarse correction is not
the limiter; and a longer outer restart ($30\!\to\!60$) is counter-productive. The
aggregate size is fixed at $3^4$ by the device tiling (the warp-padding requires the
coarse time-slice volume to be a multiple of $32$, which only the $4^4$ coarse grid
satisfies on $12^4$). The configuration of Table~\ref{tab:mg} is thus already at the
tunable optimum; further gains require an algorithmic change (additional grid
levels, a genuinely adapted aggregation) rather than parameter tuning --- again
consistent with a well-conditioned, finite-volume-limited problem in which the
coarse space has little work to do.

\begin{table}[h]
\centering
\begin{tabular}{lll}
\toprule
parameter & sweep & outer iters \\
\midrule
GMRES smoother depth $m$ & $2,3,\mathbf{4},8,16$ & $421,399,\mathbf{247},150,97$ \\
setup smoothing $N_{\mathrm{step}}$ & $\mathbf{0},1,2,3$    & $\mathbf{247},248,248,249$ \\
near-null vectors $N_v$  & $\mathbf{8},12,16,24$ & $\mathbf{247},241,238,245$ \\
coarse-solve iterations  & $\mathbf{2},5,10$     & $\mathbf{247},247,247$ \\
outer restart length     & $\mathbf{30},60$      & $\mathbf{247},286$ \\
\bottomrule
\end{tabular}
\caption{Multigrid parameter sensitivity at $m_q=0.005$, $\alpha=0.5$; boldface is
the configuration of Table~\ref{tab:mg}. Wall-clock-minimising values, not merely
iteration-count-minimising: four smoother sweeps is the time optimum despite $8$ and
$16$ giving fewer iterations.}
\label{tab:tuning}
\end{table}

\section{Future work}
\label{sec:future}

The present note establishes correctness and a residual-matched baseline. The
following programme of validation is ordered so that each inexpensive step
de-risks the more expensive ones that follow; item~1 is a prerequisite for all
of them.

\begin{enumerate}
\item \textbf{Near-null subspace setup.} The run reported here uses
$N_{\mathrm{step}}=0$ setup smoothing and $N_v=8$ vectors. The first task is to
restore an adaptive setup ($N_{\mathrm{step}}>0$, larger $N_v$) and measure the
reduction in outer iteration count, so that the AMG is assessed at its genuine
optimum rather than the present deliberately minimal configuration.

\item \textbf{Quark-mass scaling.} Measure the outer iteration count (and the
fine-operator application count) of the AMG, of unpreconditioned GMRES on $\Aop$,
and of even-odd CGNE as a function of $m_q\in\{0.01,0.005,0.002,0.001\}$ at fixed,
residual-matched tolerance. The defining property of multigrid is a near
mass-independent iteration count, set against the steep growth of CGNE as
$m_q\to0$; this scaling, not a single-point ratio, is the quantitative case for
the method.

\item \textbf{Scale-up validation.} Repeat the comparison on larger volumes and
smaller quark masses, on data-centre GPUs (A100/H100) whose memory and
batched-GEMM throughput the method is designed to exploit. The single consumer GPU
used here understates the achievable gain; this step is the quantitative basis for
a production deployment.

\item \textbf{BF16-storage smoother.} The smoother is ${\sim}65\%$ of the V-cycle
and is dominated by fine-$\Aop$ applications (Table~\ref{tab:vctime}), whose cost is
bandwidth-bound; storing the smoother's fermion field (and gauge) in
\texttt{bfloat16} with FP32 register accumulation therefore offers up to ${\sim}2\times$
on that kernel. Because the smoother is only a \emph{preconditioner}, the reduced
precision is corrected by the outer FGMRES and the FP32 residual refinement, so the
physics is untouched: an A/B test on the present setup, emulating bfloat16 rounding
of the smoother's fine-$\Aop$ output, leaves the pseudoscalar 2-point function
invariant to $5\times10^{-9}$ and the residual mass to $6\times10^{-8}$ (far below
the solver floor), with the outer V-cycle count unchanged. The optimisation is thus
\emph{de-risked}; what remains is the production kernel port (templating the fused
$C^{-1}$ and hop kernels on the storage type, confined to the smoother instance).
Like the levers above its payoff is largest at production volume, where the
fine-operator bandwidth dominates.
\end{enumerate}


\appendix
\section{Backup material}
\label{sec:backup}
This appendix collects the full treatment of the Neff $\alpha$ parameter --- the operator definition, the measured spectrum and conditioning, the $\alpha>1$ scan, and the $\alpha$-invariance check. It is logically independent of the multigrid construction, which fixes $\alpha=1$ throughout (Section~\ref{sec:target}), and is intended to be split off into a standalone note.

\paragraph{The M\"obius/Neff $\alpha$-form.} The fifth-dimension structure carries
a parameter $\alpha$ (the better-conditioned domain-wall form of Neff
\cite{NeffOriginal}, studied for solver acceleration in \cite{ChenAlpha}): in the
present operator it
multiplies the $s\!\pm\!1$ chiral shift and the wall projectors of $\Ddw$. Neff
shows \cite{NeffOriginal} that $\alpha$ leaves the four-dimensional effective
operator --- hence the boundary-wall propagator and the pion --- \emph{exactly}
invariant, while rescaling every \emph{bulk} fifth-dimension slice by one factor
of $1/\alpha$. The residual mass is therefore subtle: the conventional midpoint
estimator $m_{\mathrm{res}}=C_{J_{5q}}/C_{PP}$ is built from the bulk midpoint
slices and so scans as $1/\alpha^2$, but this is an artifact of the
reconstruction, \emph{not} physics --- the chiral-symmetry-breaking
$m_{\mathrm{res}}$ resides in the $\alpha$-free overlap kernel $(S\!-\!1)/(S\!+\!1)$
and is invariant. Restoring the compensating factor of $\alpha$ on the midpoint
current recovers an $\alpha$-invariant $m_{\mathrm{res}}$; we verify both the raw
$1/\alpha^2$ scan and its correction on the batched solver in
Section~\ref{sec:batched} (Table~\ref{tab:alpha}, Figure~\ref{fig:mres}). The
effect of $\alpha$ on the \emph{conditioning} of $\Aop$ --- which, unlike the
physics, is ensemble-dependent --- is detailed next.

\paragraph{Effect of $\alpha$ on $\Aop$ (measured).}
We measure the eigenspectrum of the single-precision $\Aop$ directly, by
implicitly-restarted Arnoldi (abs-ascending and abs-descending) on the $12^4$ test
configuration (Table~\ref{tab:spectrum}). Decreasing $\alpha$ \emph{spreads} the
spectrum: $\lambda_{\max}$ grows from $4.66$ at $\alpha\!=\!1$ to $23.8$ at
$\alpha\!=\!0.4$, $\lambda_{\min}$ rises only mildly ($3.16\to4.86\times10^{-3}$),
and $\kappa(\Aop)\equiv\lambda_{\max}/\lambda_{\min}$ rises monotonically from
$1.5\times10^3$ to $4.9\times10^3$. Both solvers track this: GMRES-on-$\Aop$ from
$391$ to $691$ iterations and the two-grid AMG from $210$ to $339$ as $\alpha$ is
lowered. The AMG offers no separate $\alpha$-acceleration; at fixed $\alpha$ it is
${\sim}2\times$ cheaper than bare GMRES ($210$ vs.\ $391$ at $\alpha=1$) and
inherits the conditioning of $\Aop$ through the Galerkin coarse operator
$\Aop_c=R\,\Aop\,P$.

\paragraph{$\alpha>1$.} We also measured $\alpha>1$. The four-dimensional physics
stays invariant: on the CGNE propagator the pseudoscalar correlator and the
corrected $m_{\mathrm{res}}$ agree with their $\alpha=1$ values to $10$--$12$
significant digits up to $\alpha=3$ (Table~\ref{tab:alpha_gt1}, left). The
conditioning degrades monotonically: bare GMRES-on-$\Aop$ is U-shaped with a flat
floor at $\alpha\!\approx\!0.8$--$1.0$ and rises to $571,\,751,\,1201$ iterations at
$\alpha=1.5,\,2.0,\,3.0$ (Table~\ref{tab:alpha_gt1}, right). No value of $\alpha$
improves on $\alpha=1$ for $\Aop$ on this configuration; \textbf{the present study
therefore fixes $\alpha=1$ throughout.}

The conditioning payoff of $\alpha$ is ensemble-dependent: on a thermalised $16^4$
configuration an $\alpha\!\approx\!0.5\text{--}0.8$ window lowers the bare
GMRES-on-$\Aop$ count by ${\sim}12\%$ \cite{ChenAlpha}, whereas the present cold
$12^4$ test gauge shows no such window and $\alpha=1$ is optimal for every solver.
The ensemble-independent statement is that $\alpha$ is a \emph{physical} knob
(Section~\ref{sec:batched}: the pion is invariant, and the residual mass is
invariant once the midpoint current carries its compensating factor of $\alpha$).

\begin{table}[h]
\centering
\begin{tabular}{ccccc}
\toprule
$\alpha$ & $\lambda_{\min}$ & $\lambda_{\max}$ & $\kappa(\Aop)$ & GMRES\,/\,AMG iters \\
\midrule
$1.0$ & $3.16\times10^{-3}$ & $4.66$ & $1.5\times10^3$ & $391\,/\,210$ \\
$0.8$ & $3.82\times10^{-3}$ & $6.07$ & $1.6\times10^3$ & $391\,/\,229$ \\
$0.6$ & $4.43\times10^{-3}$ & $10.6$ & $2.4\times10^3$ & $481\,/\,266$ \\
$0.5$ & $4.67\times10^{-3}$ & $15.2$ & $3.3\times10^3$ & $541\,/\,247$ \\
$0.4$ & $4.86\times10^{-3}$ & $23.8$ & $4.9\times10^3$ & $691\,/\,339$ \\
\bottomrule
\end{tabular}
\caption{Measured spectrum of the single-precision target operator $\Aop$ versus
the Neff $\alpha$, with the resulting iteration counts, all on the \emph{same}
$12^4$ $\beta=5.7$ cold configuration, $m_q=0.005$, $N_s=8$.
$\lambda_{\min},\lambda_{\max}$ are the extreme converged eigenvalues from
implicitly-restarted Arnoldi; $\kappa(\Aop)=\lambda_{\max}/\lambda_{\min}$. As
$\alpha$ decreases the spectrum spreads and $\kappa$ grows, and both
unpreconditioned GMRES-on-$\Aop$ and the two-grid AMG track it monotonically:
$\alpha=1$ is optimal for both on this ensemble. The AMG is uniformly ${\sim}2\times$
cheaper than bare GMRES at fixed $\alpha$.}
\label{tab:spectrum}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{cc@{\qquad}cc}
\toprule
\multicolumn{2}{c}{\emph{physics (CGNE, invariant)}} & \multicolumn{2}{c}{\emph{conditioning (GMRES-on-$\Aop$)}}\\
\cmidrule(r){1-2}\cmidrule(l){3-4}
$\alpha$ & pion / $m_{\mathrm{res}}$ agree & $\alpha$ & GMRES iters \\
\midrule
$1.0$ & --- (reference)        & $0.6$ & $481$ \\
$1.5$ & $12$ / $10$ digits     & $0.8$ & $391$ \\
$2.0$ & $12$ / $10$ digits     & $1.0$ & $391$ \\
$3.0$ & $12$ / $10$ digits     & $1.5$ & $571$ \\
      &                        & $2.0$ & $751$ \\
      &                        & $3.0$ & $1201$ \\
\bottomrule
\end{tabular}
\caption{The $\alpha\!>\!1$ measurements, same $12^4$/$m_q\!=\!0.005$/$N_s\!=\!8$.
\emph{Left:} the four-dimensional physics is invariant past $\alpha=1$ --- the
pseudoscalar correlator and the $\alpha$-corrected residual mass, measured on the
CGNE propagator, agree with the $\alpha=1$ values to $10$--$12$ significant digits
up to $\alpha=3$. \emph{Right:} the bare GMRES-on-$\Aop$ count is U-shaped, with a
flat floor at $\alpha\approx0.8$--$1.0$ and rising ${\sim}3\times$ by $\alpha=3$.
The study fixes $\alpha=1$.}
\label{tab:alpha_gt1}
\end{table}

\paragraph{The \texorpdfstring{$\alpha$}{alpha}-invariance check.}
Carrying the Neff $\alpha$-form through the \emph{physical} operator (and hence,
by the Galerkin construction, through the coarse operator) must leave the
four-dimensional pion exactly invariant. We solve the batched propagator at
$\alpha\in\{0.38,0.5,0.76,1.0,1.25\}$ on the same solver (Table~\ref{tab:alpha},
Figure~\ref{fig:mres}). The pseudoscalar correlator is invariant across the whole
range to $\sim5\times10^{-4}$ (the FP32 inner-solve floor), confirming that
$\alpha$ propagates correctly into every factor of $\Aop$ and into the Galerkin
coarse operator. The \emph{raw} midpoint residual mass varies by $\approx7\times$,
tracking the reconstruction's $1/\alpha^2$ closely for $\alpha\gtrsim0.5$; but, as
explained in Section~\ref{sec:target}, this is the bulk-slice $1/\alpha$ of the
midpoint current squared, an artifact of the estimator and not a physical shift.
Restoring the compensating factor of $\alpha$ on the midpoint density (last column
of Table~\ref{tab:alpha}, flat series in Figure~\ref{fig:mres}) collapses the scan:
the \emph{corrected} $m_{\mathrm{res}}$ is invariant to ${\sim}3\%$ for
$\alpha\gtrsim0.76$, with the residual droop at $\alpha\le0.5$ reflecting the loose
single-precision solve at the most ill-conditioned points (largest $\kappa$,
Table~\ref{tab:spectrum}) --- a numerical, not physical, effect: a tighter-converged
check at $\alpha=0.5$ recovers $m_{\mathrm{res}}$ to within $0.13\%$ of its
$\alpha=1$ value. The physically correct statement is thus that $\alpha$ leaves
both the pion \emph{and} the residual mass invariant, as a four-dimensional
observable must.

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\toprule
$\alpha$ & $C_{PP}$ & $m_{\mathrm{res}}^{\mathrm{raw}}$ & $\alpha^2 m_{\mathrm{res}}^{\mathrm{raw}}$ \\
\midrule
$0.38$ & $1.56801\times10^{-1}$ & $4.667\times10^{-1}$ & $6.74\times10^{-2}$ \\
$0.50$ & $1.56779\times10^{-1}$ & $3.500\times10^{-1}$ & $8.75\times10^{-2}$ \\
$0.76$ & $1.56751\times10^{-1}$ & $1.682\times10^{-1}$ & $9.71\times10^{-2}$ \\
$1.00$ & $1.56750\times10^{-1}$ & $9.658\times10^{-2}$ & $9.66\times10^{-2}$ \\
$1.25$ & $1.56758\times10^{-1}$ & $6.340\times10^{-2}$ & $9.91\times10^{-2}$ \\
\bottomrule
\end{tabular}
\caption{$\alpha$-scan on the batched AMG solver, $12^4$, $\beta=5.7$,
$m_q=0.005$, single precision. The pion $C_{PP}$ is invariant to the FP32 floor
across the whole range. The \emph{raw} midpoint residual mass
$m_{\mathrm{res}}^{\mathrm{raw}}$ scans by $7\times$ (the $1/\alpha^2$ artifact of
the bulk-slice reconstruction); the corrected, physical residual mass
$\alpha^2 m_{\mathrm{res}}^{\mathrm{raw}}$ is invariant to ${\sim}3\%$ for
$\alpha\gtrsim0.76$, drooping at smaller $\alpha$ only because the FP32 inner
solve is least converged where $\kappa(\Aop)$ is largest.}
\label{tab:alpha}
\end{table}

\begin{figure}[h]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=11cm, height=7cm,
    xlabel={$\alpha$}, ylabel={$m_{\mathrm{res}}$},
    xmin=0.3, xmax=1.35, ymin=0.03, ymax=0.55,
    grid=both, grid style={gray!20},
    legend pos=north east, legend cell align=left,
    tick label style={font=\small}, label style={font=\small},
]
% 1/alpha^2 reference, normalised at alpha=1 (m_res=0.09658)
\addplot[domain=0.35:1.3, samples=80, dashed, thick, gray] {0.09658/(x*x)};
\addlegendentry{$1/\alpha^2$ (normalised at $\alpha{=}1$)}
% raw measured points
\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {
  (0.38, 0.46669) (0.50, 0.35001) (0.76, 0.16817) (1.00, 0.09658) (1.25, 0.06340)
};
\addlegendentry{raw $m_{\mathrm{res}}$ (estimator)}
% corrected, alpha-invariant: alpha^2 * raw
\addplot[only marks, mark=square*, mark size=2pt, red] coordinates {
  (0.38, 0.06740) (0.50, 0.08750) (0.76, 0.09710) (1.00, 0.09658) (1.25, 0.09910)
};
\addlegendentry{corrected $\alpha^2 m_{\mathrm{res}}$ (physical)}
\end{axis}
\end{tikzpicture}
\caption{Residual mass versus the M\"obius $\alpha$ on the batched AMG solver
($12^4$, $m_q=0.005$, single precision). The dashed curve is $1/\alpha^2$
normalised at $\alpha=1$; the blue circles are the \emph{raw} midpoint estimator,
which follows it (an artifact of the $1/\alpha$ bulk-slice reconstruction). The
red squares are the \emph{corrected}, physical residual mass
$\alpha^2 m_{\mathrm{res}}$, which is $\alpha$-invariant up to the FP32 inner-solve
floor at the most ill-conditioned (small-$\alpha$) points; the pion correlator
(Table~\ref{tab:alpha}) is invariant throughout.}
\label{fig:mres}
\end{figure}

\begin{thebibliography}{9}

\bibitem{KCM2024}
I.~Kanamori, W.-L.~Chen and H.~Matsufuru,
\emph{Multigrid solver for the M\"obius domain-wall fermion with a
Pauli--Villars preconditioned target operator},
PoS \textbf{LATTICE2024} (2025) 414;
I.~Kanamori, \emph{Note on a multigrid solver for the domain-wall fermion},
unpublished design note (2023).

\bibitem{BridgeMG}
I.~Kanamori, K.-I.~Ishikawa and H.~Matsufuru,
\emph{Object-oriented implementation of an adaptive aggregation-based algebraic
multigrid method in Bridge++},
in \emph{Computational Science -- ICCS}, doi:10.1007/978-3-030-86976-2\_15
[arXiv:2111.05012].

\bibitem{DDalphaAMG}
A.~Frommer, K.~Kahl, S.~Krieg, B.~Leder and M.~Rottmann,
\emph{Adaptive aggregation-based domain decomposition multigrid for the lattice
Wilson--Dirac operator},
SIAM J.\ Sci.\ Comput.\ \textbf{36} (2014) A1581 [arXiv:1303.1377].

\bibitem{BrowerPV}
R.~C.~Brower, M.~A.~Clark, D.~Howarth and E.~S.~Weinberg,
\emph{Multigrid for chiral lattice fermions: domain wall},
Phys.\ Rev.\ D \textbf{102} (2020) 094517 [arXiv:2004.07732].

\bibitem{NeffOriginal}
H.~Neff,
\emph{A better conditioned domain-wall operator} (2015),
[arXiv:1501.04950].

\bibitem{ChenAlpha}
W.-L.~Chen, I.~Kanamori, H.~Matsufuru and H.~Neff,
\emph{Accelerating iterative linear equation solver using modified domain-wall
fermion matrix in lattice QCD simulations},
[arXiv:2602.14454].

\bibitem{BoyleYamaguchi}
P.~Boyle and A.~Yamaguchi,
\emph{Comparison of domain-wall multigrid coarsening strategies},
arXiv:2103.05034.

\bibitem{BoyleMRHS}
P.~Boyle,
\emph{Multiple right hand side multigrid for domain wall fermions},
arXiv:2409.03904.

\end{thebibliography}

\end{document}
